Photographic Text-to-Image Synthesis \\ with a Hierarchically-nested Adversarial Network

### 2017-11-13 cvpr2018.tex

@@

\textcolor{red}{We also study the effectiveness of the proposed local image loss. We conduct experiments with using architecture with side output 64$\times$64, 128$\times$128 and 256 $\times$ 256 using CUB dataset. 
As can be seen in Table\ref{tab:local_loss}, we can see that by removing local image loss (denoted as "No Local"), the inception score drop from \textcolor{red}{4.27} to \textcolor{red}{3.8}. To quantitatively compare the results, we also show generated results using two model in Figure \ref{local_or_not}, We can see that, although both models can successfully capture the semantic correspondence between image and sentence, 256$\times$ 256 results generated by model trained with local image loss provide more local fine-grained details, thus improving the visual quality. }

@@

\begin{table}[t] % retrieval
	\small
	\begin{minipage}[b]{0.5\linewidth}
			\begin{tabularx}{.98\textwidth}{c@{\hskip1pt}|c@{\hskip1pt}c@{\hskip1pt}}
				\specialrule{1.5pt}{0pt}{0pt}  
				Metric 			&   VS 	 & MS-SSMI   	\\  \hline
				w/o Img         &   $.25{\pm}.16$      &   $.215$           \\  \hline
				w/ global       &   $-$      &   $-$           \\ \hline
				w/local         &   $-$ 	 &   $-$		    \\ \hline
			\end{tabularx}
		\vspace{-0.8cm}
	\end{minipage} %\hfill
	\begin{minipage}[b]{0.49\linewidth}
		\begin{tabularx}{.98\textwidth}{ccc|c}
			\specialrule{1.5pt}{0pt}{0pt}  
			\multicolumn{3}{c|}{Components}	&  \multirow{2}{*}{\thead{Inception \\ score}}	\\ \cline{1-3}
			64	& 128	& 256 			& 		\\ \hline
			&  		&	\checkmark	&	${3.52{\pm}.04}$	\\ 
			&  	\checkmark	&	\checkmark	&	${3.99{\pm}.04}$	\\
			\checkmark	&  			&	\checkmark	&  ${4.14{\pm}.03}$		\\
			\checkmark	&  \checkmark		&	\checkmark	&	${4.15{\pm}.05}$ \\ \hline

>>>>

\begin{table}[t] % retrieval
	\small
	\begin{minipage}[b]{0.5\linewidth}
		\begin{tabularx}{1\textwidth}{c@{\hskip1pt}|c@{\hskip1pt}|c@{\hskip1pt}}
			\specialrule{1.5pt}{0pt}{0pt}  
			Metric 			&   Inception 	 & VS   	\\  \hline
			wo/local        &   $3.12{\pm}.018$      &   $.263{\pm}.13$           \\  \hline
			w/local         &   $3.45{\pm}.07$ 	 &   $.296{\pm}.13$		    \\ \hline
		\end{tabularx}
		\vspace{-0.8cm}
	\end{minipage} %\hfill
	\begin{minipage}[b]{0.49\linewidth}
		\begin{tabularx}{.98\textwidth}{ccc|c}
			\specialrule{1.5pt}{0pt}{0pt}  
			\multicolumn{3}{c|}{Components}	&  \multirow{2}{*}{\thead{Inception \\ score}}	\\ \cline{1-3}
			64	& 128	& 256 			& 		\\ \hline
			&  		&	\checkmark	&	${3.52{\pm}.04}$	\\ 
			&  	\checkmark	&	\checkmark	&	${3.99{\pm}.04}$	\\
			\checkmark	&  			&	\checkmark	&  ${4.14{\pm}.03}$		\\
			\checkmark	&  \checkmark		&	\checkmark	&	${4.15{\pm}.05}$ \\ \hline

@@

We also study the effectiveness of the proposed local image loss. We conduct experiments with using architecture with side output 64$\times$64, 128$\times$128 and 256 $\times$ 256 using Oxford dataset. 
As can be seen in Table\ref{tab:ablation}, we can see that by removing local image loss (denoted as "wo/ Local"), the inception score drop from \textcolor{red}{3.45} to \textcolor{red}{3.12}, which proven that adding local image loss can help to improve the visual quality of the generated images. Besides, local image loss also helps to improve the visual-semantic matching evidenced by the higher VS score of w/local. We hypothesis that it is because adding separate local image loss can help the pair-wise loss to focus on learning the pair-wise matching task.

\textcolor{red}{To quantitatively compare the results, we also show generated results using two model in Figure \ref{local_or_not}, We can see that, although both models can successfully capture the semantic correspondence between image and sentence, 256$\times$ 256 results generated by model trained with local image loss provide more local fine-grained details, thus improving the visual quality. }

@@
